VOI-aware Monte Carlo Sampling in Trees

### 2011-12-08 paper/vago/paper.tex
draft done

As the results show, without sample redistribution UCT is as good as
better as the VOI-aware policies for lower numbers of samples per ply
(5000, 7000), and the advantage of VOI-aware policies for larger
number of samples is rather modest (e.g., ECT wins in 55\% of games for
10000 samples per ply). For the stopping threshold of $10^-6$,
however, the VOI-aware policies are almost always better than UCT
(only VCT for 5000 samples wins in less than 50\% of games), with
stronger policies (ECT, VCT) reaching the winning rate of 66\%.

>>>>

As the results show, without sample redistribution UCT is as good as
better as the VOI-aware policies for lower numbers of samples per ply
(5000, 7000), and the advantage of VOI-aware policies for larger
number of samples is rather modest (e.g., ECT wins in 55\% of games for
10000 samples per ply). For the stopping threshold of $10^{-6}$,
however, the VOI-aware policies are almost always better than UCT
(only VCT for 5000 samples wins in less than 50\% of games), with
stronger policies (ECT, VCT) reaching the winning rate of 66\%.
